KidsAIR home activity and characteristics cleaning

### 2020-06-22 home_char_act_cleaning.Rmd
data cleaning updates

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 19 June 2020"
output: pdf_document
---

@@

kids_home_act <- rbind(wmt_home_act, nn_home_act, ak_home_act)

@@

home_act_clean <- kids_home_act %>% 
  mutate(area = as.factor(area)) %>% 
  right_join(kids_linked_ids, by = c("area", "home_winter_id"))

>>>>

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 22 June 2020"
output: pdf_document
---

@@

kids_home_act <- rbind(wmt_home_act, nn_home_act, ak_home_act) %>% 
  select(-home_act_comments)

@@

home_act_clean <- kids_home_act %>% 
  mutate(area = as.factor(area)) %>% 
  right_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  filter(!is.na(home_act_day))
